Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-17 paper/structureScene.tex
Formatting DCASE 2016 results URL

\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning}
\usepackage{url}
\usepackage{color}
\usepackage{graphicx}
\usepackage{xspace}
\newcommand*{\eg}{e.g.\@\xspace}
\newcommand*{\ie}{i.e.\@\xspace}
\newcommand*{\vs}{vs.\@\xspace}

@@

We compare our results with baseline classifier using linear SVMs and MFCC features, which achieves an average accuracy of $65.5\%$. With the scattering transform, however, the average accuracy increases to $79.4\%$. This accuracy increases slightly to $80.8\%$ when calculated on the held-out evaluation dataset.\footnote{See \url{http://www.cs.tut.fi/sgn/arg/dcase2016/task-results-acoustic-scene-classification}} The small change in accuracy suggests that there is little overfitting in the model, an indication of good generalization power.

>>>>

\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning}
\usepackage[hyphens]{url}
\usepackage{color}
\usepackage{graphicx}
\usepackage{xspace}
\newcommand*{\eg}{e.g.\@\xspace}
\newcommand*{\ie}{i.e.\@\xspace}
\newcommand*{\vs}{vs.\@\xspace}

@@

We compare our results with baseline classifier using linear SVMs and MFCC features, which achieves an average accuracy of $65.5\%$. With the scattering transform, however, the average accuracy increases to $79.4\%$. This accuracy increases slightly to $80.8\%$ when calculated on the held-out evaluation dataset.\footnote{\url{http://www.cs.tut.fi/sgn/arg/dcase2016/task-results-acoustic-scene-classification}} The small change in accuracy suggests that there is little overfitting in the model, an indication of good generalization power.
